### 2025-01-29 scripts/Paper-analysis.Rmd
more notes on analysis

```{r}
leading.region.PTUs = sort(names(PTU.min.sizes[PTU.min.sizes>20000]))
cat(leading.region.PTUs, sep="\n")
```
### Sliding window analysis

@@

>>>>

```{r}
leading.region.PTUs = sort(names(PTU.min.sizes[PTU.min.sizes>20000]))
cat(leading.region.PTUs, sep="\n")
```

For convenience for other scripts, I save some files with names of plasmids within each PTU.

```{r}
for (PTU in unique(plasmid.table$PTU)){
  cat(plasmid.table$ID[plasmid.table$PTU==PTU], sep="\n",
      file=paste0('~/Downloads/trieste/', PTU, '_plasmids.txt'))
}

```
### Sliding window analysis

@@

Test for a particular PTU.

```{r}

scores_df = read.csv('../test_bokz_k5_scores.csv', header=T)
scores_average <- scores_df %>%
  rowwise() %>%
  mutate(score_avg = mean(c_across(starts_with("score")))) %>%
  ungroup() %>%
  select(kmer, score_avg)  
# Order by average score
scores_average$kmer = ordered(scores_average$kmer,
                              levels=scores_average$kmer[order(scores_average$score_avg)])
scores.plot = ggplot(scores_average, aes(kmer, score_avg))+geom_point()+
  coord_flip()
```
